Viral Sequence Sorting Tools - Rules on Fragments

### 2023-02-20 TestingPipeline/Scripts/visualizing_rules_on_short_fragments.Rmd
added vs2 SOP v2
Compared further the keep2 category and analyzed the range of accuracy for the VS2 SOP given the manual curation is 0% or 100% accurate.

Fixed small bugs in fragments by changing the numrules to a factor data type so read as discrete not continuous

ggplot(accuracy_scores, aes(x=toolcombo, y=precision, 
                                  color=numrules, fill=numrules)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Precision") +
  scale_fill_manual(name="Number of Rules",
                     values = alpha(rev(pal(6)), 0.5)) +
  scale_color_manual(name="Number of Rules",
                     values = alpha(rev(pal(6)), 1))
```

>>>>

ggplot(accuracy_scores, aes(x=toolcombo, y=precision, 
                                  color=as.factor(numrules), fill=numrules)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Precision") +
  scale_fill_manual(name="Number of Rules",
                     values = alpha(rev(pal(6)), 0.5)) +
  scale_color_manual(name="Number of Rules",
                     values = alpha(rev(pal(6)), 1))
```
